Truthfulness Verification System

### 2011-02-23 proposal/paper.tex
corrected some grammer mistakes

\section{Introduction}
Web has became most prevalent source of information now a days. However, many
information on the web is untruthful. Also because of the widespread reach of
web, sometimes web is used to propagate untruthful facts for social and political
reasons. Hence with the increasingly use of web as information source,
verification of information truthfulness became an important facet to consider.

@@

First, T-verifier assumes that truthful statements will be more propagated in the
web compared to the untruthful statement. However, this may be not true in
general because of intended and planned propaganda for establishing some
untruthful statements. This kind of propagandas are even becoming more common now
a days due to widespread reach of Internet. T-verifier also showed that "Hillary
Clinton is the President of United States" has more hits than "Hillary Clinton is
the Secretary of State". Although T-verifier was able to find the correct
statement in this case using multiple ranks together, in general the untruthful
statement can be prevalent in the web compared to truthful statements.

@@

\subsubsection{Finding Sense using Wordnet}
To classify a statement as true or false we need to get the semantic of sense of the words of the sentences. For example consider the following sentence.

@@

>>>>

\section{Introduction}
Web has became the most prevalent source of information now a days. However, many
information on the web is untruthful. Also because of the widespread reach of
web, sometimes web is used to propagate untruthful facts for social and political
reasons. Hence with the increasingly use of web as information source,
verification of information truthfulness became an important facet to consider.

@@

First, T-verifier assumes that truthful statements will be more propagated in the
web compared to the untruthful statement. However, this may be not true in
general because of intended and planned propaganda for establishing some
untruthful statements. This kind of propagandas are even becoming more common now
a days due to widespread reach of Internet. T-verifier also showed that \emph{"Hillary
Clinton is the President of United States"} has more hits than \emph{"Hillary Clinton is
the Secretary of State"}. Although T-verifier was able to find the correct
statement in this case using multiple ranks together, in general the untruthful
statement can be prevalent in the web compared to truthful statements.

@@

\subsubsection{Finding Sense of Words}
To classify a statement as true or false we need to get the semantic of sense of the words of the sentences. For example consider the following sentence.

@@

However, finding sense of words in a complex problem in general and not easy to solve for all cases all the time. For example, consider the following sentence.

\emph{"Filipino is the primary language of Philipines"}

now Wikipedia has "Filipino is the national language of Philipines". Both sentences have same meaning but it is not easy to relate primary with national because they are not each others synonym as separate words. They become synonym depending on the context they are used such as above example. At this point, we don't have any generic strategy to handle these kind of situations. However, we will explore more to find possible ways to solve these problems. And one possible way may be to use some natural language processing techniques. Specifically, we will look into NLTK library to solve these kind of issues.
